---
title: "Stella's linear regression"
author: "Stella Zhang"
date: "2024-04-17"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install or load the packages

```{r, message=FALSE,warning=FALSE}
library(ggplot2)
library(tidyverse)
```

## Read or give the data

```{r}
Fertilizer_usage=c(50, 70, 90, 110, 130, 150, 170, 190, 210, 230,
250, 270, 290, 310, 330, 350, 370, 390, 410, 430)
Crop_yield=c(2.8, 3.4, 3.7, 4.9, 5.6, 6.2, 6.9, 7.7, 8.4, 8.9, 9.8,
10.5, 11.3, 11.8, 12.6, 13.3, 14.2, 14.8, 15.6, 16.2)

# scattrer plot
my_data1=data.frame(Fertilizer_usage,Crop_yield)

```

## Scotter plot for the data

```{r}

ggplot(my_data1,aes(x=Fertilizer_usage,y=Crop_yield))+
      geom_point()

```
## Simple linear regression

```{r}
reg_model=lm(Crop_yield~Fertilizer_usage)
summary(reg_model)

```

Since the p-value is less than $5\%$ therefore the Fertilizer Usage is a significant variable for the Crop Yield.


```{r}
my_data1=data.frame(Fertilizer_usage,Crop_yield)
ggplot(my_data1,aes(x=Fertilizer_usage,y=Crop_yield))+
 geom_point()+
  geom_smooth(method=lm)

```
## R square
```{r}
summary(reg_model)$r.squared

```

In conclusion, the Fertilizer Usage level can explain $99.92\%$ of the variability in the Crop Yield.

## Normality test

```{r}
shapiro.test(reg_model$residuals)
ks.test(reg_model$residuals,"pnorm")

```

Since the p-value for the Shapiro-Wilk test is $0.02502$, which is less than $5%$, and the p-value for the Kolmogorov-Smirnov test is $0.0005912$, also less than $5%$, the normality assumption of the error terms is not confirmed. This suggests that the error terms do not follow a normal distribution, which is a violation of one of the key assumptions of the classical linear regression model. 


```{r}
plot(reg_model)
```
## Constant variance Assumption


```{r,warning=FALSE,message=FALSE}
library(lmtest)
res<-bptest(reg_model)
res

```

Since the p-value is 0.1137, which is more than $5\%$ so the constant variance assumption is hold.

## Corrolation 
to test is there is a significant correlation between two variables, we use the **cor.test()** function in R. 

```{r}
cor.test(my_data1$Fertilizer_usage,my_data1$Crop_yield)
```

The correlation is $0.9996$ with the p-value of $2.2e-16$. since the p-value is less than $5\%$ so we reject the null hypothesis. We accept that there is a significant linear association between Fertilizer Usage and Crop Yield. 






## Install or load the packages

```{r, message=FALSE,warning=FALSE}
library(ggplot2)
library(tidyverse)
```

## Read or give the data

```{r}
Irrigation_frequency=c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13,
14, 15, 16, 17, 18, 19, 20)
Plant_height=c(10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75,
80, 85, 90, 95, 100, 105)

# scottrer plot
my_data2=data.frame(Irrigation_frequency,Plant_height)

```

## Scatter plot for the data

```{r}

ggplot(my_data2,aes(x=Irrigation_frequency,y=Plant_height))+
      geom_point()

```
## Simple linear regression

```{r}
reg_model=lm(Plant_height~Irrigation_frequency)
summary(reg_model)

```

since the p-value is less than $5\%$ therefore the Irrigation Frequency is a significant variable for the Plant Height.


```{r}
my_data2=data.frame(Irrigation_frequency,Plant_height)
ggplot(my_data2,aes(x=Irrigation_frequency,y=Plant_height))+
 geom_point()+
  geom_smooth(method=lm)

```
## R square
```{r}
summary(reg_model)$r.squared

```
The Irrigation Frequency level can explain $100\%$ of the variability on the Plant Height.

## Normality test

```{r}
shapiro.test(reg_model$residuals)
ks.test(reg_model$residuals,"pnorm")

```
Since the p-value for both the Shapiro-Wilk test $6.774e-06$ and the Kolmogorov-Smirnov test $3.788e-05$ are less than $5%$, we reject the null hypothesis. Therefore, the normality assumption of the error terms is not confirmed. This suggests that the error terms do not follow a normal distribution.


```{r}
plot(reg_model)
```
## Constant variance Assumption


```{r,warning=FALSE,message=FALSE}
library(lmtest)
res<-bptest(reg_model)
res

```
Since the p-value is $0.02434$, less than $5\%$, we reject the null hypothesis of constant variance. This indicates that the assumption of constant variance (homoscedasticity) does not hold, suggesting the presence of heteroscedasticity in the residuals.

## Corrolation 
to test is there is a significant correlation between two variables, we use the **cor.test()** function in R. 

```{r}
cor.test(my_data2$Irrigation_frequency,my_data2$Plant_height)
```
The correlation is $1$ with the p-value of less than $2.2e-16$. since the p-value is less than $5\%$, so we reject the null hypothesis. We accept that there is a significant linear association between Irrigation Frequency and Plant Height. 






## Install or load the packages

```{r, message=FALSE,warning=FALSE}
library(ggplot2)
library(tidyverse)
```

## Read or give the data

```{r}
Sunlight_exposure=c(6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17,
18, 19, 20, 21, 22, 23, 24, 25)
Fruit_weight=c(50, 60, 70, 80, 90, 100, 110, 120, 130, 140, 150,
160, 170, 180, 190, 200, 210, 220, 230, 240)

# scottrer plot
my_data3=data.frame(Sunlight_exposure,Fruit_weight)

```

## Scatter plot for the data

```{r}

ggplot(my_data3,aes(x=Sunlight_exposure,y=Fruit_weight))+
      geom_point()

```
## Simple linear regression

```{r}
reg_model=lm(Fruit_weight~Sunlight_exposure)
summary(reg_model)

```

The p-value of less than $2.2e-16$, since the p-value is significantly less than $5\%$, therefore the Sunlight Exposure is a significant variable for the Fruit Weight.


```{r}
my_data3=data.frame(Sunlight_exposure,Fruit_weight)
ggplot(my_data3,aes(x=Sunlight_exposure,y=Fruit_weight))+
 geom_point()+
  geom_smooth(method=lm)

```
## R square
```{r}
summary(reg_model)$r.squared

```
The Sunlight Exposure level can explain $100\%$ of the variability on the Fruit Weight. Although this perfect fit suggests a strong linear relationship, it raises concerns about potential overfitting, meaning the model might not perform as well on new data.

## Normality test

```{r}
shapiro.test(reg_model$residuals)
ks.test(reg_model$residuals,"pnorm")

```
since the p-value for both the Shapiro-Wilk test and the Kolmogorov-Smirnov test are less than $5%$, we reject the null hypothesis that the residuals are normally distributed. Therefore, the normality assumption of the error terms is not confirmed.


```{r}
plot(reg_model)
```
## Constant variance Assumption


```{r,warning=FALSE,message=FALSE}
library(lmtest)
res<-bptest(reg_model)
res

```
Since the p-value is $0.02473$, less than $5\%$, we reject the null hypothesis of constant variance. Therefore, the assumption of constant variance (homoscedasticity) does not hold.

## Corrolation 
to test is there is a significant correlation between two variables, we use the **cor.test()** function in R. 

```{r}
cor.test(my_data3$Sunlight_exposure,my_data3$Fruit_weight)
```
The correlation is $1$ with the p-value of less than $2.2e-16$. since the p-value is significantly less than $5\%$, we reject the null hypothesis. We accept that there is a perfect and significant linear association between Sunlight Exposure and Fruit Weight. 






## Install or load the packages

```{r, message=FALSE,warning=FALSE}
library(ggplot2)
library(tidyverse)
```

## Read or give the data

```{r}
Soil_pH_level=c(4.5, 5.0, 5.5, 6.0, 6.5, 7.0, 7.5, 8.0, 8.5, 9.0, 9.5, 10.0, 10.5, 11.0, 11.5, 12.0, 12.5, 13.0, 13.5, 14.0)
Crop_yield_b=c(3.2, 3.7, 4.0, 4.5, 5.0, 5.5, 6.0, 6.5, 7.0, 7.5, 8.0, 8.5, 9.0, 9.5, 10.0, 10.5, 11.0, 11.5, 12.0, 12.5)

# scottrer plot
my_data4=data.frame(Soil_pH_level,Crop_yield_b)

```

## Scatter plot for the data

```{r}

ggplot(my_data4,aes(x=Soil_pH_level,y=Crop_yield_b))+
      geom_point()

```
## Simple linear regression

```{r}
reg_model=lm(Crop_yield_b~Soil_pH_level)
summary(reg_model)

```

since the p-value is less than $5\%$ therefore the Soil pH Level is a significant variable for the Crop Yield.


```{r}
my_data4=data.frame(Soil_pH_level,Crop_yield_b)
ggplot(my_data4,aes(x=Soil_pH_level,y=Crop_yield_b))+
 geom_point()+
  geom_smooth(method=lm)

```
## R square
```{r}
summary(reg_model)$r.squared

```
The Soil pH level can explain approximately $99.97\%$ of the variability on the Crop Yield.

## Normality test

```{r}
shapiro.test(reg_model$residuals)
ks.test(reg_model$residuals,"pnorm")

```
since the p-value for both the Shapiro-Wilk test $0.003348$ and the Kolmogorov-Smirnov test $0.0001108$ are less than $5%$, we reject the null hypothesis. Therefore, the normality assumption of the error terms is not confirmed. This suggests that the error terms do not follow a normal distribution.


```{r}
plot(reg_model)
```
## Constant variance Assumption


```{r,warning=FALSE,message=FALSE}
library(lmtest)
res<-bptest(reg_model)
res

```
Since the p-value is $0.004176$, less than $5\%$, we reject the null hypothesis of constant variance. Therefore, the assumption of constant variance (homoscedasticity) does not hold.

## Corrolation 
to test is there is a significant correlation between two variables, we use the **cor.test()** function in R. 

```{r}
cor.test(my_data4$Soil_pH_level,my_data4$Crop_yield_b)
```
The correlation is $0.9998386$ with the p-value of less than $2.2e-16$. since the p-value is less than $5\%$ so we reject the null hypothesis. We accept that there is a perfact and significant linear association between Soil pH Level and Crop Yield. 






## Install or load the packages

```{r, message=FALSE,warning=FALSE}
library(ggplot2)
library(tidyverse)
```

## Read or give the data

```{r}
Temperature=c(10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30, 32, 34, 36, 38, 40, 42, 44, 46, 48)
Germination_time=c(7, 6.8, 6.5, 6.2, 6, 5.8, 5.5, 5.3, 5.2, 5, 4.8, 4.7, 4.5, 4.3, 4.2, 4.1, 4, 3.8, 3.7, 3.5)

# scottrer plot
my_data5=data.frame(Temperature,Germination_time)

```

## Scatter plot for the data

```{r}

ggplot(my_data5,aes(x=Temperature,y=Germination_time))+
      geom_point()

```
## Simple linear regression

```{r}
reg_model=lm(Germination_time~Temperature)
summary(reg_model)

```

since the p-value is less than $5\%$ therefore the Temperature is a significant variable for the Germination Time.


```{r}
my_data5=data.frame(Temperature,Germination_time)
ggplot(my_data5,aes(x=Temperature,y=Germination_time))+
 geom_point()+
  geom_smooth(method=lm)

```
## R square
```{r}
summary(reg_model)$r.squared

```
The Temperature level can explain $98.3\%$ of the variability on the Germination Time.

## Normality test

```{r}
shapiro.test(reg_model$residuals)
ks.test(reg_model$residuals,"pnorm")

```
since the p-value for the Shapiro-Wilk test is $0.2081$, higher than $5\%$, this test does not reject the null hypothesis of normality. However, the Kolmogorov-Smirnov test's p-value is $0.0008911$, significantly less than $5\%$, which rejects the null hypothesis of normality.Therefore, The normality of the residuals is not conclusively confirmed. There is evidence suggesting that the residuals may not be normally distributed.


```{r}
plot(reg_model)
```
## Constant variance Assumption


```{r,warning=FALSE,message=FALSE}
library(lmtest)
res<-bptest(reg_model)
res

```
Since the p-value is $0.1287$, more than $5\%$, so the constant variance assumption is hold.

## Corrolation 
to test is there is a significant correlation between two variables, we use the **cor.test()** function in R. 

```{r}
cor.test(my_data5$Temperature,my_data5$Germination_time)
```
The correlation is $-0.991$ with the p-value of $2.2×10−16$. since the p-value is less than $5\%$ so we reject the null hypothesis. We accept that there is a strong and significant negative linear association between Temperature and Germination Time. 





